
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------
	
	\cvmyentry
	{Hybrid Image Learning and Classification Architecture} % Job title
	{\vspace{-2.0mm} Oct. 2015 - March 2016} % Date(s)
	{	\vspace*{-\baselineskip} \vspace{+2.0mm}
	\begin{cvitems} % Description(s) of tasks/responsibilities
		Designed and developed a hybrid novel architecture which shall speed up image classification and facilitate future upgrades. It uses deep-neural networks (Caffe framework) along with SVMs and other AI techniques (OpenCV framework) and uses MongoDB database at its core. 
	\end{cvitems}
	}
	
	%---------------------------------------------------------

	
	%---------------------------------------------------------
	
	\cvmyentry
	{Web-Application for Food Management} % Job title
	{\vspace{-2.0mm} Nov. 2015 - Jan. 2016} % Date(s)
	{	\vspace*{-\baselineskip} \vspace{+2.0mm}
		\begin{cvitems} % Description(s) of tasks/responsibilities
			Created a web application in a team which helps users to save food and suggest recipes based on groceries they already have. Application hosted on google-cloud based on Python, JavaScript & Angular. (
				 %\urlstyle{same}
				 \url{https://cloudappdevg.appspot.com}
				 )
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	
	
	%---------------------------------------------------------
	
	\cvmyentry
	{Custom compiler and functional language} % Job title
	{\vspace{-2.0mm} March. 2015 - June. 2016} % Date(s)
	{	\vspace*{-\baselineskip} \vspace{+2.0mm}
		\begin{cvitems} % Description(s) of tasks/responsibilities
			Designed and implemented a custom compiler written in OCaml for our own language, in pair. Created an evaluator for Scheme which helped me gain valuable insight into functional programming.
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	
	
	%---------------------------------------------------------
	
	\cvmyentry
	{AI Game Solver} % Job title
	{\vspace{-2.0mm} Oct. 2014 - Dec. 2014} % Date(s)
	{	\vspace*{-\baselineskip} \vspace{+2.0mm}
		\begin{cvitems} % Description(s) of tasks/responsibilities
			Created an AI game solver which solves the 8 / 16 puzzle. Created both Heuristic and Blind searches.
		\end{cvitems}
	}
	
	%---------------------------------------------------------

	
	%---------------------------------------------------------
	
	\cvmyentry
	{Java based projects} % Job title
	{\vspace{-2.0mm} Oct. 2013 - June. 2015} % Date(s)
	{	\vspace*{-\baselineskip} \vspace{+2.0mm}
		\begin{cvitems} % Description(s) of tasks/responsibilities
				Designed and Built a complete Auction \& Messaging system (Both server and front end application), Distributed power system chain (Smart Meter), Fractal creation algorithm and underlying GUI, Bee hive Simulation. Also in group of 4 people, we designed and created an Advertisement dashboard which has many complex features presented with a fully functional UI (Using Agile Methodologies)
		\end{cvitems}
	}
	
	%---------------------------------------------------------

	
\end{cventries}
